### 2014-11-07 tex/lazy.tex
writing the initialization

The rewrite rule to initialize a heap in the symbolic summarization
technique is shown in~\figref{fig:initHeap}. The set $\mathbb{UN}$

 There are three
constraint-location pair sets $\theta_\mathit{null}$,
$\theta_\mathit{new}$, and $\theta_\mathit{alias}$ that correspond to
the non-deterministic choices in GSE. The $\theta_\mathit{null}$ creates
a constraint location pair where the constraint under which the field is read $\phi_x$ $l_\mathit{null}$

@@

The access on $l_0.x$ creates a new input reference $r_1^i$ in the
summary heap shown in~\figref{fig:initHeap}(b). The reference $r_1^1$
points to the $l_\mathit{null}$ location under the constraint that
$r_1^i$ is null: $\phi_{1a} := r_1^i = r_\mathit{null}$. The reference
$r_1^i$ points to the location $l_1$ under the constraint that $r_1^i$
is not null $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The location
$l_1$ represents a fresh location of type $C$ is created on the heap
such that $C$ is type of $\mathit{this}.x$.

>>>>

The rewrite rule to initialize a heap in the symbolic summarization
technique is shown in~\figref{fig:symInit}. Given the unitialized set
$\mathbb{UN}$ for field $f$, the $\mathit{min}_l$ function returns the
constraint location pair based on a lexical ordering of locations. The
init$_r$ method returns a new input reference $r_f$ while the
fresh$_f$ returns a new location of type $C$. The set $\rho$ contains
the set of reference location, $(r_a, l_a)$, pairs that the current
field may alias. The pair $(r_a, l_a)$ is contained in the set $ \rho
$ if $r_a$ is part of the input references initialized in the summary
heap, $r_a$ is in the pre-image of $l_a$, and the type of $l_a$ is the
same as the type of the field being initialized then the pair $(r_a,
l_a)$ is added to the $\rho$ set.

There are three constraint-location pair sets that correspond to
non-deterministic choices in GSE: (a) $\theta_\mathit{null}$ that
creates a constraint that states $r_f$ is null under which it points
to $l_\mathit{null}$, (b) $\theta_\mathit{new}$ the constraint that
$r_f$ is not null and it does not alias another reference in set
$\rho$ under which it points to the newly created location $l_f$, (c)
and $\theta_\mathit{alias}$ where for each element in the set $(r_a,
l_a) \in \rho$ it creates a constraints that $r_f$ is not null, points
to $r_a$, and does not point to any reference contained in
$(r_a^\prime, l_a^\prime) \in \rho$ such that $r_a \neq
r_a^\prime$. Additionally $\theta_\mathit{orig}$ allows for the
possibility that the field continues to remain uninitialized since the
heap is symbolic. We refer to this initialization in the summary
machine as conditional initialization. Finally, the fields of the
reference $r_f$ are marked as uninitialized.

In the post condition of the rule the reference $r_f$ points to
$\theta$ which contains the union of all the constraint location pairs
sets, and the field $f$ points to the new reference $r_f$ in the
summary heap.  Note that the summarize rule invoked repeatedly until
the set of unitialized constraint location pairs for field $f$ is
empty. In other words the set $\lambda$ is empty. This consititutes
the summarize end rule in~\figref{fig:symInit}.

@@

The access on $l_0.x$ creates a new input reference $r_1^i$ in the
summary heap shown in~\figref{fig:initHeap}(b). The reference $r_1^1$
points to the $l_\mathit{null}$ location under the constraint that
$r_1^i$ is null: $\phi_{1a} := r_1^i = r_\mathit{null}$. The reference
$r_1^i$ points to the location $l_1$ under the constraint that $r_1^i$
is not $\mathit{null}$ $\phi_{1b} :=r_1^i \neq r_\mathit{null}$. The
location $l_1$ represents a fresh location of type $C$ is created on
the heap such that $C$ is type of $\mathit{this}.x$.

Following the initialization to the $\mathit{this}.x$, when we
initialize $\mathit{this}.y$ the resulting summary heap is shown
in~\figref{fig:initHeap}(c). The set $\rho$ shown
in~\figref{fig:initHeap}(d) contains the potential aliases for
$\mathit{this}.y$ which is location $l_1$ ($\mathit{this}.x$). The
constraint location $\theta$ sets represents the initialization
choices for $\mathit{this}.y$. The new input reference $r_2^i$ for
$this.y$ points to (a) location $l_\mathit{null}$ under the constraint
$\phi_{2a} := r_2^i = r_\mathit{null}$, (b) location $l_2$ under the
constraint $\phi_{2b} := r_2^i \neq r_\mathit{null} \wedge r_2^i \neq
r_1^i$ that states that $r_2^i$ is not null and does not alias
$r_1^i$, and (c) location $l_1$ under the constraint $\phi_{2c} :=
r_2^i \neq r_\mathit{null} \wedge r_2^i = r_1^i$ that states $r_2^i$
is not null and \emph{does} alias $r_1^i$.
